\documentclass[class=article, crop=false]{standalone}

\begin{document}
Marine plastic pollution is a large issue these days. Removal of marine plastic pollution is sadly an underrepresented topic in research and development. This report continues work on a simulation and control system intended for a solution that will remove marine plastics. The system consists of an unmanned surface vessel and a negatively-buoyant remotely operated vehicle with a gripper attached. Because the remotely operated vehicle is negatively buoyant, the two vesssels are coupled, meaning that the movements of one inherently affects the movements of the other. This provides interesting control challenges.

In this project, a simulator and control system have continued development from a previously made baseline, and the system has been simulated in various sea states. The results show that the controller is currently not tuned well enough and that the simulation has some work to be done, but the results are nonetheless promising.

\vspace{20pt}

\hrule

\vspace{20pt}

Plast i havet er et stort problem i moderne tid, men det er relativt lite forskning når det kommer til fjerning av havplast. Denne rapporten fortsetter arbeid fra et tidligere prosjekt, med fokus på simulering og kontroll av en løsning for å fjerne havbunnsplast. Løsningen, som ble fremmet i det tidligere prosjektet, består av et ubemannet overflatefartøy og et fjernstyr undervannsfartøy. Undervannsfartøyet har negativ oppdrift, som gjør at systemet av overflatefartøyet og undervannsfartøyet blir koblet. Det vil si at krefter som påvirker den ene parten også vil påvirke den andre. Dette fører til interessante problemer for et kontrollsystem.

I dette prosjektet har simulatoren og kontrolleren fra det tidligere prosjektet blitt videreutviklet og testet i mer komplisert sjø. Resultatene av simuleringen viser at kontrolleren trenger mer justering for å bli brukbar og at simuleringen har mangler. Allikevel er resultatene lovende for fremtidig arbeid.

%Write an abstract/summary of your thesis, and state your main findings here. \\

%\noindent A summary should be included in both English and any second language, if this is applicable, regardless if the thesis is written in English or in your preferred language. These should be on separate pages, the English version first.

\end{document}
