\documentclass[class=article, crop=false, draft=true]{standalone}
\usepackage{graphicx}
\graphicspath{{../Figures}}

\usepackage{cleveref}

\begin{document}
%equations, bib. \\
\section{Previous project work}
This report is in a way a continuation of a specialization project\cite{specialization} done previously. The specialization project was focused on setting up a framework to work with. Part of hte specialization project has been starting work on a simulator that can be used to work on a control system. The control system is currently rudimentary implemented but there is room for improvement. The goal of the development for the conttrol sytemis to have it be platform agnostic. That is, the control system does not care whether tis' connected to a simulator or a vessel in hte real world. TThe way this is ideally implemented is by using ROS2. ROS2 is a framework to control robotics, built around publishers and subscribers that all act around topics.



\section{State of the Art}
\subsection{Physical issues}
\subsection{Simulation issues}

\section{Mathematical basis}

\section{Modelling and Control Design}

\section{Navigation}
Alternatives for underwater navigation
\subsection{GNSS}
Only used above water
\subsection{Taut-wire positioning}
Mention taut wire, how it is usable somewhat btu not really because the ROV is not heavy enough to have the wire taut
\subsection{USBL}
Available and accurate

Need to consider limitations of accuracy of USBL re: salinity, water temperature/density, etc.

\end{document}
